PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
add the employmen to the data merging

glad/edgi data frame list
```{r glad/edgi data frame list}
if(GLAD == TRUE | EDGI == TRUE) {
dfs.list <- list(
  dem.raw.id,
  prepan.gad.raw.id,
  mhd.raw.categories,
  prepan.ocir.raw.id,
  prepan.pcl.raw.id,
  prepan.phq.raw.id,
  coping.gad.raw.id,
  coping.pcl.raw.id,
  coping.phq.raw.id,
  coping.ocir.raw.id
)
}
```

>>>>

glad/edgi data frame list
```{r glad/edgi data frame list}
if(GLAD == TRUE | EDGI == TRUE) {
dfs.list <- list(
  dem.raw.id,
  employment.raw.id,
  mhd.raw.categories,
  prepan.gad.raw.id,
  prepan.pcl.raw.id,
  prepan.phq.raw.id,
  prepan.ocir.raw.id,
  coping.gad.raw.id,
  coping.pcl.raw.id,
  coping.phq.raw.id,
  coping.ocir.raw.id
)
}
```
